Home Nighttime Cough Monitoring

### 2025-03-06 Lilah Melzer/cough_monitor_analysis.qmd
cough monitor saved figures

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
library(gt)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor")
```

@@

label(demo$pre_fev_pp) <- "Post-bronchodilator FEV1 % Predicted"

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
f <- as.formula(paste0("Diagnosis ~", paste0(colnames(demo), collapse = "+")))
f <- update(f, . ~ . - Diagnosis - sid)
t1 <- tableby(f, data = demo, control = mycontrols)
summary(t1, pfootnote = T)
```

@@

```{r}
#| label: fig-coughs-dist
#| fig-cap: Histogram of Coughs Across All Nights
#| warning: false
ggplot(agg_counts, aes(x = Coughs)) +
  geom_histogram(binwidth = 1)
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by nights from start
#| warning: false
ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid), color = Diagnosis
)) +
  geom_point(alpha = 0.1) +
  geom_line(alpha = 0.1) +
  geom_smooth(aes(group = Diagnosis)) +
  theme_bw()
```

@@

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
library(gt)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

label(demo$post_fev_pp) <- "Post-bronchodilator FEV1 % Predicted"

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
t1 <- tableby(Diagnosis ~ nih_sex + age_at_consent + height_perc + weight_perc +
  nih_race + nih_ethnicity + cftr_mod + cftr_mod_type + Genotype + pre_fev_pp +
  total_sleep, data = demo, control = mycontrols)
summary(t1, pfootnote = T)
```

@@

```{r}
#| label: fig-coughs-dist
#| fig-cap: Histogram of Coughs Across All Nights
#| warning: false
hist <- ggplot(agg_counts, aes(x = Coughs)) +
  geom_histogram() +
  theme_bw() +
  theme(axis.title.y = element_blank())
hist
ggsave(paste0(home_dir, "/Dissemination/Figures/histogram.png"),
  plot = hist, width = 9, height = 6, units = "in"
)
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by nights from start
#| warning: false
fig2 <- ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid), color = Diagnosis
)) +
  geom_point(alpha = 0.1) +
  geom_line(alpha = 0.1) +
  geom_smooth(aes(group = Diagnosis)) +
  theme_bw()
fig2
ggsave(paste0(home_dir, "/Dissemination/Figures/fig2.png"),
  plot = fig2, width = 9, height = 6, units = "in"
)
```

@@

## Association with coughs

There were no statistically significant correlations between coughs and survey scores.

# Participant figures

```{r}
#| warning: false
cfqr_children_6_11$sid <- as.numeric(cfqr_children_6_11$sid)
cfqr_parent_6_13$sid <- as.numeric(cfqr_parent_6_13$sid)
p38 <- full_join(
  agg_counts,
  cfqr_children_6_11 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Children Ages 6-11` = respirat),
  by = join_by(sid, Date)
)
p38 <- full_join(
  p38,
  cfqr_parent_6_13 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Caregivers 6-13` = respirat),
  by = join_by(sid, Date)
)
p38 <- p38 %>%
  filter(sid == 38) %>%
  pivot_longer(c(Coughs, `CFQ-R Children Ages 6-11`, `CFQ-R Caregivers 6-13`)) %>%
  filter(!is.na(value))
p38$name <- factor(p38$name,
  levels = c("Coughs", "CFQ-R Children Ages 6-11", "CFQ-R Caregivers 6-13")
)
p38_plot <- ggplot(p38, aes(x = Night, y = value)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  facet_wrap(~name, nrow = 3, scales = "free")
p38_plot
ggsave(paste0(home_dir, "/Dissemination/Figures/participant_38.png"),
  plot = p38_plot, width = 9, height = 7, units = "in"
)
```
